Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-12 talk/pepm2011/paper.tex
(cfbolz, arigo) Abstract.

\maketitle
\begin{abstract}
\footnote{This research is partially supported by the BMBF funded project PyJIT (nr. 01QE0913B;
Eureka Eurostars).}
\end{abstract}

@@

In this paper, we used a approach based on partial evaluation to
optimize allocations in the traces of a tracing JIT.  In this context a
simple approach to partial evaluation gives good results.  This is due
to the fact that the tracing JIT itself is responsible for all control
issues, which are usually the hardest part of partial evaluation: the
tracing JIT selects the parts of the program that are worthwhile to
optimize, and extracts linear paths through them, inlining functions as
necessary.  What is left to optimize is only those linear paths.

>>>>

\maketitle
\begin{abstract}
The performance of many dynamic language implementations suffers from
high allocation rates and runtime type checks.  This makes dynamic
languages less applicable to purely algorithmic problems, despite their
growing popularity.  In this paper, we present a simple optimization
based on online partial evaluation to remove object allocations and
runtime type checks in the context of a tracing JIT.  We evaluate the
optimization using a Python VM and find that it gives good results for
all our (real-life) benchmarks.
\footnote{This research is partially supported by the BMBF funded project PyJIT (nr. 01QE0913B;
Eureka Eurostars).}
\end{abstract}

@@

In this paper, we used a approach based on online partial evaluation to
optimize allocations in the traces of a tracing JIT.  In this context a
simple approach to partial evaluation gives good results.  This is due
to the fact that the tracing JIT itself is responsible for all control
issues, which are usually the hardest part of partial evaluation: the
tracing JIT selects the parts of the program that are worthwhile to
optimize, and extracts linear paths through them, inlining functions as
necessary.  What is left to optimize is only those linear paths.
